%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Karrer CV/Resume
% XeLaTeX Template
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Isaac}{Karrer}{ % Your name
\urlstyle{same}\url{http://github.com/imkarrer} \\ % Your website, LinkedIn profile or other web address
\href{mailto:isaac.karrer@gmail.com}{isaac.karrer@gmail.com} | 512.619.9994 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{Georgia Tech}
\descript{Masters of Science, Computer Science}
\location{Attended Aug 2016 - May 2018}
15 hours completed\\ 

\sectionspace

\subsection{Texas State University}
\descript{BS in Computer Science}
\location{May 2014 | San Marcos, Tx \\ Major GPA: 3.8}
Math Minor \\
College of Engineering \\
Dean's List (Fall 13, Spring 14) \\

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{LBJ LASA}
Liberal Arts \& Science Academy \\
\location{Grad. May 2005 | Austin, Tx}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Coursework
%------------------------------------------------

\subsection{Coursework}

Software Test and Analysis \\
High Performance Computer Arch \\
Computer Security \\
Data Mining \\
Data Compression \\
Networks \\
Data Structures \\
Object Oriented Design

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}

\location{Frameworks}
scalatest \textbullet{} terraform \textbullet{} Selenium \textbullet{} Kitura \\
\sectionspace
\location{Proficient Languages}
Scala \textbullet{} Java \textbullet{} Python \textbullet{} Bash \\

\sectionspace
\location{Familiar Languages}
Golang \textbullet{} Ruby \textbullet{} C++ \textbullet{} MySQL \\

\sectionspace

\subsection{Deployment/CI}
Jenkins \textbullet{} Bamboo\\
Gradle \textbullet{} Docker \textbullet{} Vagrant\\ 

\sectionspace % Some whitespace after the section

\subsection{Cloud Services}
elasticsearch \textbullet{} AWS \textbullet{} GCP \textbullet{} Azure\\
IBM Softlayer \textbullet{} Oracle CRM DB\\


%----------------------------------------------------------------------------------------

\section{Related Interests}
\sectionspace % Some whitespace after the section
\begin{tightitemize}
\item Scuba Diving
\item DIY Home and Car Maintenance
\item R/C Cars, Planes, and Quadcopters
\end{tightitemize}


\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{elasticsearch}
\location{| Senior Software Engineer}
\location{April 2018 - Current | Remote }
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Implemented Release Exit Check quality gate to assert the health of our public cloud as we released across cloud providers and their regions.
\item Teams started adding tests to the Release Exit Checks when they saw we could catch things as the release progressed.  Adding an annotation to a test was all that was required to add it to the release.
\item Ownership of Release Exit Checks distributed to teams who owned the test.
\item cloud-sdk-java for consuming Elasticsearch Service in java projects. 
\item Implemented patterns for initializing swagger api controllers as the desired persona and authentication strategy in the scalatest framework.
\item Implemented key primitives in the scalatest framework to facilitate migrating system tests from the ClustersApi to the DeploymentsApi.  Teams quickly completed the migration when the ClustersApi was EOL.
\item Executed tactical refactors to simplify the maintenance burden of scalatests.
\item Worked the customer facing support queue as a platform admin to debug, triage, and remidate broken elasticsearch deployments on Elasticsearch Service and Elastic Cloud Enterprise.
\end{tightitemize}

\sectionspace % Some whitespace after the section

\runsubsection{JAMF}
\location{| Software Engineer II}
\location{October 2015 - March 2018 | Eau Claire, WI}
\begin{tightitemize}
\item Key contributor to new system testing framework.
\item Implemented REST client for legacy Customer API using Spring and JaxB
\item Led team of 5 others to automate existing manual regression suite.
\item Automated reporting of Test Results into TestRail using Python.
\item Implemented component tagging scheme to ensure that every test could be expedited to a development team for triage when failures occured.
\item Led intern project to expose the MacOS Accessbility API via a REST server implemented in Swift so that we could control applications on the screen after a VNC session had been established.
\item Implemented Client Reservation Server using Spring Boot, Docker, and Gradle.  Used MySQL, H2, and Swagger Code Gen.  Service has been in production for 1+ year with 99.99\% availabilty.
\end{tightitemize}

\sectionspace % Some whitespace after the section

\runsubsection{IBM}
\location{| Cloud Infrastrucutre Services - Software Engineer}
\location{May 2014 – June 2015 | Austin, TX}
\begin{tightitemize}
\item Deployed OpenStack Object Storage using Chef
\item Wrote an automated capacity manager using Python for OpenStack Swift
\item Automated Ring building for OpenStack Swift using Chef
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{San Francisco Consulting Group}

\location{Software Engineering Intern}
\location{May 2013 – Sept 2013 | Austin, TX}
\begin{tightitemize}
\item Wrote PHP and jQuery to perform custom CRUD operations
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{City of Austin Parks and Recreation Parks Division}
\location{Supervisor, Manager, Maintenance, Lifeguard Instructor}
\location{May 2004 – Aug 2012 | Austin, TX}
\begin{tightitemize}
\item 9 years management, leadership, and teaching experience
\item Managed and trained 70+ ARC Lifeguards across 6 sites
\end{tightitemize}

% \sectionspace % Some whitespace after the section

% \subsection{Entrepreneurship}The Classic Garage
% \location{| Eau Claire, WI}
% \location{June 2015 - Current}
% %\vspace{\topsep} % Hacky fix for awkward extra vertical space
% \begin{tightitemize}
% \item Increased organization and efficiency to cut payroll by 35\%
% \item Responsible for a perfect score on the State Health Department inspection
% \end{tightitemize}
% West Texas Wings 
% \location{| Alpine, TX}
% \location{June 2012 - July 2012}
% \begin{tightitemize}
% \item Developed a website to host the menu and increased revenue by 17\%
% \item Responsible for 94/100 on the State Health Department inspection
% \end{tightitemize}
%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}
